---
title: "INFO on Universities in the United States"
author: "Hanjiang Xu, Risa Nabari, Jett Chang-Lam"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Dynamic

* Please insert your dynamic paragraph here!!



## ACCESSING THE /source DIRECTORY
### Example 1: Source some code and run a function
```{r, message = FALSE}
# Example 1: Note relative path, which can be read: Up one
# directory(..), down into source (/source), and 
# then "source" an R file (data_access.R)
source("../source/Calculated Summary information.R")
summary_info
```

### Example 2: Initialize a variable and then use it
```{r, include=FALSE}
# Example 1: This function was "sourced" above
```

> Hope you have a good day!! 

## Table

In the following summary table, we include information including Average undergraduate enrollment, average admit rate, and average SAT submission rate of each state across the United States. The table is organized in descending order based on the average undergraduate enrollment, and it will only show the first ten states for this report. 
```{r ehco = FALSE, results='asis', message = FALSE, echo=FALSE}
source("../source/Table of summary information.R")
library(knitr)
kable(head(college_table_rename[1:4], n = 10), caption = "Basic informaion of Universities of the first ten states based on enrollment" )
```

## Charts
Following are the three charts we computed for our project: 

Chart #1: 

```{r, echo=FALSE}
source("../source/Chart #1.R")
```

Descriptive paragraph: 
The purpose of chart 1 is to present the average expense for the out of state students in each state.
This gives the students insights to how expensive it may cost to attend and live in each state, which could 
give an idea to the students if they would like to apply the college/university based on their own economic status. 

Chart #2: Average university SAT submit rate of each state
```{r, echo=FALSE}
source("../source/Chart #2.R")
```

